### 2014-06-03 ACL2014/experiments.tex
updating experiments

\section{Experiments}
We evaluate our  distributed large-scale approximate near neighbor framework by conducting 
several experiments on publicly available query logs as well as a 
large-scale query log collected from a commercial search engine.

@@

\subsection{Data}
The public dataset that we demonstrate results on is adapted from the query logs of the AOL search engine \cite{Pass06}  (\aol dataset). 
Moreover, we show results on a large query log (hundreds of millions of queries) sampled from a commercial search engine. 
We started by collecting a dataset over multiple days, and containing $N=600$ million unique queries: this does not represent
an exhaustive set of queries posed to the search engine. We then created multiple datasets from this corpus by subsampling it at various rates.
\dataA represents a $1\%$ sample of queries from the above corpus, \dataB represents a $10\%$ sample and \dataC represents the entire corpus. 
For each query, a high dimensional and sparse, feature vector was created over the domain of urls (the size of the domain is a few billion).   
The feature vector of a query $q$ contains the  webpages (urls) that have received a user click for this search query $q$. The weight of 
an url feature for a query $q$ depends on the click through rate of this url for the query $q$.  
As a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

>>>>

\section{Experiments}
In this section, we illustrate experimental results to evaluate our distributed neighbor search framework.
Our experiments are conducted on publicly available query logs collected from the AOL search engine~\cite{Pass06} as well as a 
large-scale query log from a commercial search engine.

@@

\subsection{Data}
The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, we perform evaluations using a large query log 
%(hundreds of millions of queries) 
from a commercial search engine, denoted as Qlogs. 
As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates. \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query, a high dimensional and sparse, feature vector was created over the domain of urls (the size of the domain is a few billion).   
The feature vector of a query $q$ contains the  webpages (urls) that have received a user click for this search query $q$. The weight of 
an url feature for a query $q$ depends on the click through rate of this url for the query $q$.  
As a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.
